### 2023-01-24 files/Chapter3/femconvergence.tex
chapter 3 last section finished

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Convergence of eigenvalues in Finite Element Analysis}
In this section, the work in the textbook \cite[p.228-236]{SF73} is discussed.\\

Let $H$ be a Hilbert space with the inner product $(\cdot,\cdot)$ and induced norm $||\cdot||$. Let $V$ be a linear subspace of $H$, with inner product defined by the bilinear form $b(\cdot,\cdot)$. It is assumed that this bilinear form $b$ is symmetric.

@@

\subsection{Preparatory theory and notation}
Some theory is required that is presented in \cite{SF73}.\\

@@

@@

From the textbook \cite{ORXX}, the following approximation for finite elements is given verbatim:
\newtheorem*{Interpolation}{Theorem}
\begin{Interpolation}[The Interpolation Theorem for Finite Elements] 
	Let $\Omega$ be an open bounded domain in $\mathcal{R}^n$ satisfying the cone condition. Let $k$ be a fixed integer and $m$ an integer such that $0\leq m \leq k+1$. Let $\Pi \in L(H^{k+1}(\Omega), H^{m}(\Omega))$ be such that
	\begin{eqnarray}
	    \Pi u = u \ \ \ \ \textrm{ for all } u \in \mathcal{P}_k(\Omega)
	\end{eqnarray}
	Then for any $u \in H^{k+1}(\Omega)$ and for sufficiently small $h$, there exists positive a constant $C$, independent of $u$ and $h$, such that
	\begin{eqnarray}
	    ||u - \Pi u||_{H^m(\Omega)} \leq C \frac{h^{k+1}}{p^m} |u|_H^{k+1}(\Omega)
	\end{eqnarray}
	where $|u|_H^{k+1}(\Omega)$ is the seminorm.
\end{Interpolation}

For the requirements of this dissertation, this is too general and can be simplified with assumptions. The first assumption is a reiteration that the eigenvalue problem is one-dimensional. Another assumption is that the basis of $S^h$ consists of polynomials. With these assumptions, the semi-norm $|u|_H$ is equal to the norm $||u||$. This approximation theorem can be rewritten as
\newtheorem{Interpolation_2}{Theorem}
\begin{Interpolation_2}
	Suppose there exists an integer $k$ such that for each element
	\begin{equation*}
		s(\Pi_e) + 1 \leq k \leq r(\Pi_e) +1.
	\end{equation*}
	Then there exists a constant $C$ such that for any $u \in C^k_+(I)$,
	\begin{equation*}
		||(\Pi u)^(m) - u^(m)|| \leq C h^{k-m} || u^(k)|| \ \text{ for } m = 0,1,...,k.
	\end{equation*}
\end{Interpolation_2}

@@

\subsection{Convergence of the eigenfunctions}
The next step is to show the convergence of the eigenfunctions. First consider the following result.

@@

\newtheorem{Lem_7}[Lem_1]{Lemma} \label{Lem_7}
\begin{Lem_7}
	\begin{eqnarray*}
		||Pu - QPu||^{2} &\leq & {\rho}^{2} ||u_{m} - Pu_{m}||^{2}
	\end{eqnarray*}
\end{Lem_7}
\begin{proof}

Using Lemma \ref{Lem_6}:
\begin{eqnarray*}
||Pu - \beta u_{m}^{h}||^{2} &=& \sum_{j\neq m} \left(\frac{\lambda_{m}}{|\lambda_{m} - \lambda_{j}^{h}|}\right)^{2} ( u_{m} - Pu_{m} ,u_{j}^{h})^{2},\\
				&\leq & \rho^{2} \sum_{j\neq m} ( u_{m} - Pu_{m} ,u_{j}^{h})^{2}, \\
				&\leq & \rho^{2} \sum_{j=1}^{N} ( u_{m} - Pu_{m} ,u_{j}^{h})^{2}, \\
				& = & \rho^{2} ||u - Pu||^{2}.\\
\end{eqnarray*}
\end{proof}

\newtheorem{Lem_8}[Lem_1]{Lemma} \label{Lem_8}
\begin{Lem_8}
	\begin{eqnarray*}
		||u_{m} - \beta u_{m}^{h}|| &\leq & \left(1+\rho\right)||u_{m}-Pu_{m}||
	\end{eqnarray*}
\end{Lem_8}
\begin{proof}
	\begin{eqnarray*}
	||u_{m} - \beta u_{m}^{h}|| & \leq & ||u_{m}-Pu_{m}|| + ||Pu_{m} - \beta u_{m}^{h}|| \\
				& \leq & \left(1+\rho\right)||u_{m}-Pu_{m}|| \ \ \textrm{ (by Lemma \ref{Lem_7})}
	\end{eqnarray*}
\end{proof}

@@

Therefore t $||u_{m} -  u_{m}^{h}|| \leq Ch^{k}||u^{k}||$. So for any $\epsilon >0$ , a $\delta >0$ can be found such that if $h < \delta$, $||u_{m} -  u_{m}^{h}|| < \epsilon$.

******************************\\
WAT IS N en WAT IS $\beta$?\\
********************************\\

\subsection{Weak variational form}
For all $f,g \in T(\Omega)$ and $h \in C(\Omega)$, define the bilinear forms
\begin{eqnarray*}
	c(f,g) & = & \iint_\Omega f \cdot g \ dA, \\
\end{eqnarray*}
and integral
\begin{eqnarray*}
	(h,g) & = & \iint_\Omega h \cdot g \ dA. \\
\end{eqnarray*}
Recall from section  that the bilinear form $b$ is defined as
\begin{eqnarray*}
	b(u,\phi) & = & \frac{1}{\gamma(1-\nu^2)}\iint_{\Omega} (\partial_1 u_1 \partial_1 \phi_1 + \partial_2 u_2 \partial _2 \phi_2 + \nu\partial_1 u_1 \partial_2\phi_2 + \nu \partial_2 u_2 \partial_1 \phi_1 ) \ dA \\
	& + & \frac{1}{2\gamma(1+\nu)}\iint_{\Omega} (\partial_1 u_2 \partial_1 \phi_2 + \partial_1 u_2 \partial_2 \phi_1 + \partial_2 u_1 \partial_1\phi_2 + \partial_2 u_1 \partial_2\phi_1) \ dA.
\end{eqnarray*}

Define the inertia space $V$ as the closure of $T(\Omega)$ in $H := H^1(0,1)\times H^1(0,1)$. Denote $X = L^2(0,1)\times L^2(0,1)$. The inertia space is $W  = X$ with norm $||\cdot||_W = \sqrt{c(\cdot,\cdot)}$.

\subsubsection{Problem 2D-1W}
Find a function $u$ such that for all $t>0$, $u(t) \in V$ and $u''(t) \in W$, satisfying the following equation
\begin{eqnarray}
	c(u''(t),v) + b(u(t),v) & = & (Q(t),v)_X \ \ \ \textrm{ for each } v \in V.
\end{eqnarray}

\end{document}

>>>>

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Convergence of eigenvalues in Finite Element Analysis}
In this section, the work in the textbook \cite[p.228-236]{SF73} is discussed. The results are the same as given in the textbook, how ever the proofs are expanded for clarity.\\

Let $H$ be a Hilbert space with the inner product $(\cdot,\cdot)$ and induced norm $||\cdot||$. Let $V$ be a linear subspace of $H$, with inner product defined by the bilinear form $b(\cdot,\cdot)$. It is assumed that this bilinear form $b$ is symmetric.\\

The following eigenvalue is given in \cite{SF73}. It is important to note that the problem is limited to one-dimensional problems.

@@

\subsection{Preliminary theory and notation}
Some theory is required before the main results can be proven. The theory is from \cite{SF73}.\\

@@

\subsubsection{The approximation theorem}

@@

From the textbook \cite{ORXX}, the following approximation theorem for finite elements is given verbatim:
\newtheorem*{Interpolation}{Theorem}
\begin{Interpolation}[The Interpolation Theorem for Finite Elements] 
	Let $\Omega$ be an open bounded domain in $\mathcal{R}^n$ satisfying the cone condition. Let $k$ be a fixed integer and $m$ an integer such that $0\leq m \leq k+1$. Let $\Pi \in L(H^{k+1}(\Omega), H^{m}(\Omega))$ be such that
	\begin{eqnarray}
	    \Pi u = u \ \ \ \ \textrm{ for all } u \in \mathcal{P}_k(\Omega)
	\end{eqnarray}
	Then for any $u \in H^{k+1}(\Omega)$ and for sufficiently small $h$, there exists positive a constant $C$, independent of $u$ and $h$, such that
	\begin{eqnarray}
	    ||u - \Pi u||_{H^m(\Omega)} \leq C \frac{h^{k+1}}{p^m} |u|_H^{k+1}(\Omega)
	\end{eqnarray}
	where $|u|_H^{k+1}(\Omega)$ is the seminorm.
\end{Interpolation}

For the requirements of this dissertation, this can be simplified with assumptions. The first assumption is a reiteration that the eigenvalue problem is one-dimensional. Another assumption is that the basis of $S^h$ consists of polynomials. With these assumptions, the semi-norm $|u|_H$ is equal to the norm $||u||$. This approximation theorem can be rewritten as
\newtheorem{Interpolation_2}{Theorem}
\begin{Interpolation_2}
	Suppose there exists an integer $k$ such that for each element
	\begin{equation*}
		s(\Pi_e) + 1 \leq k \leq r(\Pi_e) +1.
	\end{equation*}
	Then there exists a constant $C$ such that for any $u \in C^k_+(I)$,
	\begin{equation*}
		||(\Pi u)^(m) - u^(m)|| \leq C h^{k-m} || u^(k)|| \ \text{ for } m = 0,1,...,k.
	\end{equation*}
\end{Interpolation_2}

This will be referred to as the approximation theorem in this section.\\

\subsubsection*{Properties of eigenvalues}

@@

\subsection{Convergence of the eigenfunctions}
The next step is to show the convergence of the eigenfunctions. The problem can be formulated using the following result.

@@

To simplify the notation, let $\beta = (Pu_m,Pu_m^h)$.

\newtheorem{Lem_7}[Lem_1]{Lemma} \label{Lem_7}
\begin{Lem_7}
	\begin{eqnarray*}
		||Pu - \beta Pu^h_m||^{2} &\leq & {\rho}^{2} ||u_{m} - Pu_{m}||^{2}
	\end{eqnarray*}
\end{Lem_7}
\begin{comment}
\begin{proof}

Using Lemma \ref{Lem_6}:
\begin{eqnarray*}
||Pu - \beta u_{m}^{h}||^{2} &=& \sum_{j\neq m} \left(\frac{\lambda_{m}}{|\lambda_{m} - \lambda_{j}^{h}|}\right)^{2} ( u_{m} - Pu_{m} ,u_{j}^{h})^{2},\\
				&\leq & \rho^{2} \sum_{j\neq m} ( u_{m} - Pu_{m} ,u_{j}^{h})^{2}, \\
				&\leq & \rho^{2} \sum_{j=1}^{N} ( u_{m} - Pu_{m} ,u_{j}^{h})^{2}, \\
				& = & \rho^{2} ||u_m - Pu_m||^{2}.\\
\end{eqnarray*}
\end{proof}
\end{comment}

\newtheorem{Lem_8}[Lem_1]{Lemma} \label{Lem_8}
\begin{Lem_8}
	\begin{eqnarray*}
		||u_{m} - \beta u_{m}^{h}|| &\leq & \left(1+\rho\right)||u_{m}-Pu_{m}||
	\end{eqnarray*}
\end{Lem_8}
\begin{comment}
\begin{proof}
	\begin{eqnarray*}
	||u_{m} - \beta u_{m}^{h}|| & \leq & ||u_{m}-Pu_{m}|| + ||Pu_{m} - \beta u_{m}^{h}|| \\
				& \leq & \left(1+\rho\right)||u_{m}-Pu_{m}|| \ \ \textrm{ (by Lemma \ref{Lem_7})}
	\end{eqnarray*}
\end{proof}
\end{comment}

The proofs for lemma's \ref{Lem_7} and \ref{Lem_8} are given in \cite{SF73}.\\

@@

Therefore t $||u_{m} -  u_{m}^{h}|| \leq Ch^{k}||u^{k}||$. So for any $\epsilon >0$ , a $\delta >0$ can be found such that if $h < \delta$, $||u_{m} -  u_{m}^{h}|| < \epsilon$.
\end{document}
